Generation of TypeScript Declaration Files from JavaScript Code

### 2020-08-27 programming-2021/main.tex

>>>>

The implementation and the results are available under the following repositories:

\begin{itemize}
  \item \url{https://github.com/proglang/run-time-information-gathering/tree/v1.1}
  \item \url{https://github.com/proglang/ts-declaration-file-generator/tree/v1.1}
  \item \url{https://github.com/proglang/ts-declaration-file-generator-service/tree/v1.1}
  \item \url{https://github.com/proglang/dts-generate-method/tree/v1.1}
  \item \url{https://github.com/proglang/dts-generate-results/tree/v1.1}
\end{itemize}
